---
title: "Exploring My Job Hunt"
author: "Charley Cowens"
date: "`r Sys.Date()`"
output:
  html_document: 
      toc: true
  pdf_document:
      toc: true
  word_document: default
always_allow_html: true
params:
  AfterThisDate: "2023-12-31"
  BoardToUse: "My Application Tracker"
  DaysToWaitForReject: 40
---


```{r packages, include=FALSE}
if(!require(dplyr)) {install.packages("dplyr"); library(dplyr)}
if(!require(kableExtra)) {install.packages("kableExtra"); library(kableExtra)}
if(!require(stringr)) {install.packages("stringr"); library(stringr)}
if(!require(tm)) {install.packages("tm"); library(tm)}
if(!require(ggplot2)) {install.packages("ggplot2"); library(ggplot2)}
if(!require(wordcloud2)) {install.packages("wordcloud2"); library(wordcloud2)}
if(!require(DiagrammeR)) {install.packages("DiagrammeR"); library(DiagrammeR)}
if(!require(ggplot2)) {install.packages("ggplot2"); library(ggplot2)}
if(!require(webshot)) {install.packages("webshot"); library(webshot)}
if(!require(lubridate)) {install.packages("lubridate"); library(lubridate)}
if(!require(maps)) {install.packages("maps"); library(maps)}
```



```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)

make_stats_table <- function(use_this, my_col_name) {
  data.frame(x = unclass(summary(use_this))) %>% 
  mutate(x = round(x, 1)) %>% 
  rename(!!my_col_name := 1) %>% 
  kable() %>% kable_styling("bordered", position="left", full_width = FALSE) %>% 
  row_spec(0, bold=T)  
}

if(!is_phantomjs_installed()) install_phantomjs(force=TRUE)
the_cards <- readRDS(paste0(params$BoardToUse,".rds")) %>% 
  filter(ApplyDate>as.Date(params$AfterThisDate) | Status == "Preparing")
```

> **`r nrow(filter(the_cards, Status != "Preparing"))` applications sent after this date: `r as.Date(params$AfterThisDate)`**

## Flow Diagrams

<details closed><summary> How the flow from Trello status to status works</summary>

```{r diagram1}
mermaid("
graph LR
    A(Preparing) -->|Sent| B{Applied}
    B -->|Arranged| C{Interview}
    B -->|Bounced| D[Rejected]
    C -->|Notified| D
    C -->|Notified| E{Offer}
    C -->|Waited long enough| F[No Response]
    B --> |Waited long enough| F
    E --> |Yes| G[Acceptance]
    E --> |No| H[Declined]
    style D fill:#f00
    style F fill:#f00
    style H fill:#f00
  ")
```
</details>

<details closed><summary>Current count for each status bucket</summary>
```{r diagram2}
mermaidscript <- paste0(
"graph LR
    A(", "Preparing ", sum(the_cards$Status=='Preparing'), 
    ") --> B{Applied ", sum(the_cards$Status=='Applied'),
    "}
    B --> C{Interview ", sum(the_cards$Status=='Interview'), 
    "}
    B --> D[Rejected ", sum(the_cards$Status=='Rejected'), 
    "]
    C -->|", sum(the_cards$Status=='Rejected' & !is.na(the_cards$InterviewedLast)),  
    "| D
    C --> E{Offer ", sum(the_cards$Status=='Offer'),
    "}
    C -->|", sum(the_cards$Status=='No Response' & !is.na(the_cards$InterviewedLast)), 
    "| F[No Response ", sum(the_cards$Status=='No Response'), 
    "]
    B --> F
    E --> G[Acceptance ", sum(the_cards$Status=='Acceptance'),
    "]
    E --> H[Declined ", sum(the_cards$Status=='Declined'),
    "]
  ")
mermaid(mermaidscript)
```
</details>

## Weekly Applications

```{r weekly apps}

apps_by_week <- filter(the_cards, !(ApplyWeek == "")) %>% 
  group_by(`Week Starting` = ApplyWeek) %>% 
  summarise(Apps=n()) 

make_stats_table(apps_by_week$Apps, "Apps per week")

ggplot(apps_by_week, aes(x=`Week Starting`, y=Apps)) + 
  theme_bw() +
  geom_segment(aes(x=`Week Starting`, 
                   xend=`Week Starting`, 
                   y=0, 
                   yend=Apps)) + 
  geom_point(size=4, color="green") + 
  labs(title="Applications by Week" ) + 
  theme(axis.text.x = element_text(angle=65, hjust=1, margin=margin(3, 0, 0, 0, "pt")))+
  scale_y_continuous(breaks = seq(0, max(apps_by_week$Apps), by = 2))

```

## Days to Apply from Creating Trello Ticket

```{r daysapply}
applications <- the_cards %>%  
  filter(!Status=="Preparing") %>% 
  mutate(DaysToApply = as.numeric(ApplyDate-CardCreated))

make_stats_table(applications$DaysToApply, "Days")

ggplot(applications, aes(DaysToApply)) + 
  theme_light() +
  geom_bar(fill="green")
```

<details closed><summary>**Apps sorted by days to apply**</summary>

```{r daysapplytable, echo=FALSE}
applications %>% 
  select(Job, Company, DaysToApply) %>%
  arrange(DaysToApply) %>% 
  kable() %>% kable_styling("striped", position="left", full_width = FALSE) %>% 
row_spec(0, bold=T)
```

</details>

## Age of Pending Applications

```{r dayspending}
pending <- the_cards %>%  
  filter(Status =="Applied") %>% 
  mutate(DaysPending = as.numeric(today()-ApplyDate))
```

How many days have the **`r nrow(pending)`** currently unresolved applications been awaiting a response? When a pending application has gotten "too old" (`r params$DaysToWaitForReject` days pending), it should be checked to move to the "No Response" status.


```{r dayspendingpresentation}
make_stats_table(pending$DaysPending, "Days")

ggplot(pending, aes(DaysPending)) + 
  theme_light() +
  geom_bar(fill="yellow")
```

<details closed><summary>**Apps sorted by how many days unresolved since application (descending)**</summary>

```{r dayspendingtable, echo=FALSE}

CountOfOld <- nrow(filter(pending, DaysPending > params$DaysToWaitForReject))
pending %>% 
  select(Job, Company, DaysPending) %>%
  arrange(desc(DaysPending)) %>% 
  kable() %>% kable_styling("striped", position="left", full_width = FALSE) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(1:CountOfOld, color="red")
```

</details>

## Days to Explicit Rejection

```{r rejection}
rejects <- the_cards %>%  
  filter(!is.na(Rejected)) %>% 
  mutate(DaysToReject = as.numeric(Rejected-ApplyDate))
```

For the `r nrow(rejects)` explicit rejections so far, how many days after application was the email received?

```{r rejectionpresentation}
make_stats_table(rejects$DaysToReject, "Days")

ggplot(rejects, aes(DaysToReject)) + 
  theme_light() +
  geom_bar(fill="red")


```

<details closed><summary>**Apps sorted by days to explicit rejection (descending)**</summary>

```{r rejectiontable}

rejects %>% 
  select(Job, Company, DaysToReject) %>%
  arrange(desc(DaysToReject)) %>% 
  kable() %>% kable_styling("striped", position="left", full_width = FALSE) %>% 
row_spec(0, bold=T)

```
</details>

## Job Titles

### Titles

#### Top 5

```{r titlestable}
df <- the_cards %>% 
  group_by(`Job Title`=Job) %>%
  summarise(Count=n()) %>% 
  arrange(desc(Count))

df %>%
  head(5) %>% 
  kable() %>% kable_styling("striped", position="left", full_width = FALSE) %>% 
row_spec(0, bold=T)

```

<details closed><summary>**Other titles in descending order**</summary>

```{r titlestable2}
df %>%
  tail(-5) %>% 
  kable() %>% kable_styling("striped", position="left", full_width = FALSE) %>% 
row_spec(0, bold=T)

```

### Keywords

```{r keywords}

# Define your character vector
text_vector <- the_cards$Job %>% str_remove_all("[:punct:]") 
corpus <- Corpus(VectorSource(text_vector)) %>% tm_map(removeWords, stopwords("english"))
dtm <- as.data.frame(as.matrix(DocumentTermMatrix(corpus)))
words <- colSums(dtm)
df <- data.frame(Word=names(dtm), Freq=words) %>% arrange(desc(Freq))

wordcloud2(data=df, size=.5, color='random-light', gridSize = 50)

```

## Locations

These are locations for the company office I would be associated with.

<details closed><summary>**City locations sorted by number of apps (descending)**</summary>

```{r locationsbycity}
the_cards %>% 
  group_by(City, State, Country) %>%
  summarise(Count=n(), Percentage = paste0(round(Count/nrow(.) * 100), "%")) %>% 
  arrange(desc(Count)) %>% 
  kable() %>% kable_styling("striped", position="left", full_width = FALSE) %>% 
row_spec(0, bold=T)
```
</details>

<details closed><summary>**US state locations sorted by number of apps (descending)**</summary>
```{r locationsbystate}

the_cards %>% 
  filter(Country=="US") %>% 
  group_by(State) %>%
  summarise(Count=n(), Percentage = paste0(round(Count/nrow(.) * 100), "%")) %>% 
  arrange(desc(Count)) %>% 
  kable() %>% kable_styling("striped", position="left", full_width = FALSE) %>% 
row_spec(0, bold=T)

# use the maps package to get a table that matches the 2-letter abbreviations I use to
#   the spelled-out state names
abbreviations <- state.fips %>% select(abb,polyname) %>% 
  mutate(polyname = ifelse(str_detect(polyname,":"),str_extract(polyname,"^.*(?=:)"),polyname)) %>% 
  distinct()

# add these names to an applications-count-for-each-state dataframe
state_counts <- the_cards %>% 
  filter(Country=="US") %>% 
  group_by(State) %>%
  summarise(Count=n()) %>% 
  left_join(abbreviations, by=c("State" = "abb")) 

#associate the counts with the mapping data for states
map_data_for_states <- map_data("state") %>%
  left_join(state_counts, by = c("region" = "polyname"))

#draw the map
ggplot(map_data_for_states, aes(x = long, y = lat, group = group, fill = Count)) +
  geom_polygon(color = "white") +
  scale_fill_gradient(low = "#ccccff", high = "#0000ff", na.value = "grey50") +
  theme_void() +
  labs(title = "US Map with Color Shading Based on Applications by State",
       fill = "Count")
```
</details>

<details closed><summary>**Country locations sorted by number of apps (descending)**</summary>
```{r locationsbycountry}
the_cards %>% 
  group_by(Country) %>%
  summarise(Count=n(), Percentage = paste0(round(Count/nrow(.) * 100), "%")) %>% 
  arrange(desc(Count)) %>% 
  kable() %>% kable_styling("striped", position="left", full_width = FALSE) %>% 
row_spec(0, bold=T)


```
</details>

## More Than One App at a Company

These are companies I've applied at more than once.

```{r morethanoneapp}
multiapps <- the_cards %>% 
  group_by(Company) %>% 
  summarise(Applications = n()) %>% 
  arrange(desc(Applications)) %>% 
  filter(Applications > 1)

multiapps %>% 
  kable() %>% kable_styling("striped", position="left", full_width = FALSE) %>% 
  row_spec(0, bold=T)
```

<details><summary>**Job specifics for these**</summary>
```{r morethanoneappdetails}
multiapps %>% 
  left_join(the_cards) %>%
  select(Company, Job, ApplyDate, Status) %>% 
  kable() %>% kable_styling("striped", position="left", full_width = FALSE) %>% 
  row_spec(0, bold=T)

```
</details>