---
title: "Exploring My Job Hunt"
author: "Charley Cowens"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
  word_document: default
always_allow_html: true
params:
  AfterThisDate: "2023-12-31"
---


```{r packages, include=FALSE}
if(!require(dplyr)) {install.packages("dplyr"); library(dplyr)}
if(!require(kableExtra)) {install.packages("kableExtra"); library(kableExtra)}
if(!require(stringr)) {install.packages("stringr"); library(stringr)}
if(!require(tm)) {install.packages("tm"); library(tm)}
if(!require(ggplot2)) {install.packages("ggplot2"); library(ggplot2)}
if(!require(wordcloud2)) {install.packages("wordcloud2"); library(wordcloud2)}
if(!require(DiagrammeR)) {install.packages("DiagrammeR"); library(DiagrammeR)}
if(!require(ggplot2)) {install.packages("ggplot2"); library(ggplot2)}
if(!require(webshot)) {install.packages("webshot"); library(webshot)}
if(!require(lubridate)) {install.packages("lubridate"); library(lubridate)}
```



```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)

make_stats_table <- function(use_this, my_col_name) {
  data.frame(x = unclass(summary(use_this))) %>% 
  mutate(x = round(x, 1)) %>% 
  rename(!!my_col_name := 1) %>% 
  kable() %>% kable_styling("bordered", position="left", full_width = FALSE) %>% 
  row_spec(0, bold=T)  
}

if(!is_phantomjs_installed()) install_phantomjs(force=TRUE)
the_cards <- readRDS("the_cards.rds") %>% 
  filter(ApplyDate>as.Date(params$AfterThisDate) | Status == "Preparing")
```

> **`r nrow(filter(the_cards, Status != "Preparing"))` applications after this date: `r as.Date(params$AfterThisDate)`**

## Flow Diagrams

<details closed><summary> How the flow from Trello status to status works</summary>

```{r diagram1}
mermaid("
graph LR
    A(Preparing) -->|Sent| B{Applied}
    B -->|Arranged| C{Interview}
    B -->|Bounced| D[Rejected]
    C -->|Notified| D
    C -->|Notified| E{Offer}
    C -->|Waited long enough| F[No Response]
    B --> |Waited long enough| F
    E --> |Yes| G[Acceptance]
    E --> |No| H[Declined]
    style D fill:#f00
    style F fill:#f00
    style H fill:#f00
  ")
```
</details>

<details closed><summary>Current count for each status bucket</summary>
```{r diagram2}
mermaidscript <- paste0(
"graph LR
    A(", "Preparing ", sum(the_cards$Status=='Preparing'), 
    ") --> B{Applied ", sum(the_cards$Status=='Applied'),
    "}
    B --> C{Interview ", sum(the_cards$Status=='Interview'), 
    "}
    B --> D[Rejected ", sum(the_cards$Status=='Rejected'), 
    "]
    C -->|", sum(the_cards$Status=='Rejected' & !is.na(the_cards$InterviewedLast)),  
    "| D
    C --> E{Offer ", sum(the_cards$Status=='Offer'),
    "}
    C -->|", sum(the_cards$Status=='No Response' & !is.na(the_cards$InterviewedLast)), 
    "| F[No Response ", sum(the_cards$Status=='No Response'), 
    "]
    B --> F
    E --> G[Acceptance ", sum(the_cards$Status=='Acceptance'),
    "]
    E --> H[Declined ", sum(the_cards$Status=='Declined'),
    "]
  ")
mermaid(mermaidscript)
```
</details>

## Weekly Applications

```{r weekly apps}

apps_by_week <- filter(the_cards, !(ApplyWeek == "")) %>% 
  group_by(`Week Starting` = ApplyWeek) %>% 
  summarise(Apps=n()) 

make_stats_table(apps_by_week$Apps, "Apps per week")

ggplot(apps_by_week, aes(x=`Week Starting`, y=Apps)) + 
  theme_bw() +
  geom_segment(aes(x=`Week Starting`, 
                   xend=`Week Starting`, 
                   y=0, 
                   yend=Apps)) + 
  geom_point(size=4, color="green") + 
  labs(title="Applications by Week" ) + 
  theme(axis.text.x = element_text(angle=65, hjust=1, margin=margin(3, 0, 0, 0, "pt")))+
  scale_y_continuous(breaks = seq(0, max(apps_by_week$Apps), by = 2))

```

## Days to Apply from Creating Trello Ticket

```{r daysapply}
applications <- the_cards %>%  
  filter(!Status=="Preparing") %>% 
  mutate(DaysToApply = as.numeric(ApplyDate-CardCreated))

make_stats_table(applications$DaysToApply, "Days")

ggplot(applications, aes(DaysToApply)) + 
  theme_light() +
  geom_bar(fill="green")
```

<details closed><summary>Apps sorted by days to apply</summary>

```{r daysapplytable, echo=FALSE}
applications %>% 
  select(Job, Company, DaysToApply) %>%
  arrange(DaysToApply) %>% 
  kable() %>% kable_styling("striped", position="left", full_width = FALSE) %>% 
row_spec(0, bold=T)
```

</details>

## Age of Pending Applications

How many days have active unresolved applications been awaiting a response? Those that are too old will have been moved to the "No Response" status. 

```{r dayspending}
pending <- the_cards %>%  
  filter(Status =="Applied") %>% 
  mutate(DaysPending = as.numeric(today()-ApplyDate))

make_stats_table(pending$DaysPending, "Days")

ggplot(pending, aes(DaysPending)) + 
  theme_light() +
  geom_bar(fill="yellow")
```

<details closed><summary>Apps sorted by how many days unresolved since application</summary>

```{r dayspendingtable, echo=FALSE}
pending %>% 
  select(Job, Company, DaysPending) %>%
  arrange(DaysPending) %>% 
  kable() %>% kable_styling("striped", position="left", full_width = FALSE) %>% 
row_spec(0, bold=T)
```

</details>

## Days to Explicit Rejection

```{r rejection}
rejects <- the_cards %>%  
  filter(!is.na(Rejected)) %>% 
  mutate(DaysToReject = as.numeric(Rejected-ApplyDate))

make_stats_table(rejects$DaysToReject, "Days")

ggplot(rejects, aes(DaysToReject)) + 
  theme_light() +
  geom_bar(fill="red")


```

<details closed><summary>Apps sorted by days to explicit rejection</summary>

```{r rejectiontable}

rejects %>% 
  select(Job, Company, DaysToReject) %>%
  arrange(DaysToReject) %>% 
  kable() %>% kable_styling("striped", position="left", full_width = FALSE) %>% 
row_spec(0, bold=T)

```
</details>

## Job Titles

### Titles

```{r titlestable}
the_cards %>% 
  group_by(`Job Title`=Job) %>%
  summarise(Count=n()) %>% 
  arrange(desc(Count)) %>% 
  kable() %>% kable_styling("striped", position="left", full_width = FALSE) %>% 
row_spec(0, bold=T)

```

### Keywords

```{r keywords}

# Define your character vector
text_vector <- the_cards$Job %>% str_remove_all("[:punct:]") 
corpus <- Corpus(VectorSource(text_vector)) %>% tm_map(removeWords, stopwords("english"))
dtm <- as.data.frame(as.matrix(DocumentTermMatrix(corpus)))
words <- colSums(dtm)
df <- data.frame(Word=names(dtm), Freq=words) %>% arrange(desc(Freq))

wordcloud2(data=df, size=.5, color='random-light', gridSize = 50)


# Add column names

count_occurrences <- function(strings, vector) {
  counts <- sapply(strings, function(x) sum(str_count(vector, x)))
  data.frame(Contains = strings, Count = counts, row.names = NULL)
}


```

## Locations

These are locations for the company office I would be associated with.

```{r locationstable}
the_cards %>% 
  group_by(Location) %>%
  summarise(Count=n()) %>% 
  arrange(desc(Count)) %>% 
  kable() %>% kable_styling("striped", position="left", full_width = FALSE) %>% 
row_spec(0, bold=T)

```